---
title: "R Notebook"
output: html_notebook
---

# set seeds

```{r}
set.seed(123)
seeds <- sample.int(2147483647, 10)

```


# dummy phases

```{r}
N <- 5 # number of phases
P <- paste0('P', 1:N) # name of phases
C <- 5 # number of components
E <- LETTERS[1:C] # name of elements


# Chemical compositions
set.seed(seeds[1])
W <- runif(N * C) %>>%
  matrix(nrow = N, ncol = C, dimnames = list(P, E)) %>>%
  `/`(rowSums(.)) %>>%
  `*`(100) %>>%
  return

# Modal compositions
set.seed(seeds[2])
M <- runif(N) %>>%
  `/`(sum(.))
```

# dummy machine conditions

```{r}
sensitivity <- 100
```


# Create required directories

```{r dir.create}
c('.map', '.map/1', '.qnt', '.qnt/.cnd') %>>%
  lapply(dir.create, showWarnings = FALSE) %>>%
  invisible()
```

# Create mapping data (.map directory)

## 0.cnd

```{r}
x_start <- 0 # mm
y_start <- 0 # mm
x_num <- 100 # number of pixels in x-axis
y_num <- 100 # number of pixels in y-axis
xy_num <- x_num * y_num
x_step <- 1000 # um
y_step <- 1000 # um
dwell <- 100 # msec
beam_map <- 1e-7 # A

data.frame(
  val = c(
    x_start,
    y_start,
    x_num,
    y_num,
    x_step,
    y_step,
    dwell,
    beam_map
  ),
  var = c(
    'Measurement Start Position X [mm]', 
    'Measurement Start Position Y [mm]', 
    'X-axis Step Number [1~1024]', 
    'Y-axis Step Number [1~1024]',
    'X Step Size [um], or Beam Dots Width',
    'Y Step Size [um], or Beam Dots Width',
    'Dwell Time [msec]',
    'Probe Current Avg, Before After [A]'
  ),
  stringsAsFactors = FALSE
) %>>%
  fwrite('.map/1/0.cnd', sep = ' ', quote = FALSE)

```

## Modal map

```{r}
set.seed(seeds[3])
map_P <- sample.int(N, xy_num, replace = TRUE, prob = M)

ggplot(
  data.frame(
    expand.grid(
      x = x_num:1,
      y = y_num:1
    ),
    Phases = P[map_P]
  )
) +
  geom_raster(aes(x = x, y = y, fill = Phases)) +
  coord_fixed() +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0))
```

## X-ray map (*_map.txt)

```{r}
set.seed(seeds[4])

rpois(xy_num * C, c(W[map_P, ]) * sensitivity * dwell * 1e-3 * beam_map * 1e+6) %>>% 
  matrix(nrow = xy_num, ncol = C) %>>% 
  as.data.frame %>>% 
  lapply(matrix, nrow = y_num, ncol = x_num) %>>% 
  lapply(as.data.table) %>>% 
  map2(paste0('.map/1/', 1:length(.), '_map.txt'), fwrite, sep = ' ', col.names = FALSE) %>>%
  invisible()

```


## .pm files

```{r}
invisible(file.create(paste0('.map/1/', 1:C, '.', E, '.pm'), showWarnings = FALSE))
```


# Create quantification data (.qnt directory)

## Settings

elemw.cnd

```{r}
beam_qnt <- 1e-8 # A
pk_t <- 10 # sec
bg_t <- 5 # sec
bgp_pos <- 1
bgm_pos <- 1


list(
  val = c(bgp_pos, bgm_pos, pk_t, bg_t),
  var = c('Back +[mm]', 'Back -[mm]', 'Peak Meas. Time [sec]', 'Back Meas. Time [sec]')
) %>>%
  lapply(rep, C) %>>%
  as.data.frame %>>%
  fwrite('.qnt/.cnd/elemw.cnd', sep = ' ', col.names = FALSE, quote = FALSE)


```

## Which pixels are quantified?

```{r}

set.seed(seeds[5])
seeds2 <- sample.int(2147483647, N)
table_phase <- c(table(map_P))
size = ifelse(table_phase < 20, table_phase, 20)
quantified_points <- lapply(
    1:N,
    function(i) {
      set.seed(seeds2[i])
      which(map_P == i)[sample.int(table_phase[i], size[i])]
    }
  ) %>>%
  unlist(use.names = FALSE, recursive = FALSE)

n <- length(quantified_points)
id <- 1:n
```

## Mass concentrations

wt.qnt

```{r}

W_qnt <- W[map_P[quantified_points], ]
cbind(id, ncol(W_qnt), W_qnt, rowSums(W_qnt)) %>>%
  as.data.frame %>>%
  fwrite('.qnt/wt.qnt', sep = ' ', col.names = FALSE) %>>%
  invisible
```


## X-ray intensities

pkint.qnt, bgp.qnt, bgm.qnt, net.qnt

```{r}
n <- length(quantified_points)

pk_cps_E <-  c(W_qnt) * sensitivity * beam_qnt * 1e+6

set.seed(seeds[6])
rpois(C * n * 3, rep(c(pk_t, bg_t / 100, bg_t / 100), each = C * n) * pk_cps_E) %>>%
  matrix(nrow = 3, ncol = C * n, byrow = TRUE) %>>%
  `/`(c(pk_t, bg_t, bg_t)) %>>%
  t %>>%
  as.data.frame %>>%
  setNames(c('pkint', 'bgp', 'bgm')) %>>%
  mutate(net = pkint - (bgp * bgp_pos + bgm * bgm_pos) / (bgp_pos + bgm_pos)) %>>%
  `/`(beam_qnt * 1e+6) %>>%
  lapply(matrix, nrow = n, ncol = C) %>>%
  lapply(function(x) cbind(id, ncol(x), x, rowSums(x))) %>>%
  lapply(as.data.frame) %>>%
  setNames(paste0('.qnt/', names(.), '.qnt')) %>>%
  map2(names(.), fwrite, sep = ' ', col.names = FALSE) %>>%
  invisible()

```

## Elements

elem.qnt and elint.qnt

```{r}
data.frame(
  id,
  length(E),
  matrix(rep(E, each = n), nrow = n, ncol = C)
) %>>%
  fwrite('.qnt/elint.qnt', sep = ' ', col.names = FALSE) %>>%
  invisible

data.frame(
  id,
  length(E),
  matrix(rep(E, each = n), nrow = n, ncol = C)
) %>>%
  fwrite('.qnt/elem.qnt', sep = ' ', col.names = FALSE) %>>%
  invisible


```


## Stage

stg.qnt

```{r}
data.frame(
  id = id,
  user = 'test',
  sample = 'test',
  id2 = id,
  x = (quantified_points %/% y_num + 1) * x_step * 1e-3,
  y = (quantified_points %% y_num + 1)  * y_step * 1e-3,
  z = 1,
  aux1 = 0,
  aux2 = 0,
  comment = paste0('P', map_P[quantified_points])
) %>>%
  fwrite('.qnt/stg.qnt', sep = ' ', col.names = FALSE) %>>%
  invisible
```


## Measurement

mes.qnt

```{r}
data.frame(
  id = id,
  a = 1,
  beam_qnt
) %>>%
  fwrite('.qnt/mes.qnt', sep = ' ', col.names = FALSE) %>>%
  invisible
```


# quantify

```{r}
library(qntmap)
wd <- getwd()
dir_map <- paste0(wd, '/.map/1')
xmap <- qltmap_load(dir_map, renew = TRUE)
qnt <- qnt_load(renew = TRUE)
centers <- qltmap_cls_centers(qnt = qnt, qltmap = xmap, dir_map = dir_map)
cls <- qltmap_cls_pois(centers, xmap, wd = dir_map)
qntmap <- qntmap_quantify(
  dir_map = dir_map,
  qnt = qnt,
  cluster = cls,
  fine_phase = NULL #Specify phase whose grain size tend to be smaller than mapping probe diameter.
)
```

```{r}
W
qntmap
```


